Operator evolution from the similarity renormalization group and the Magnus expansion

### 2020-06-19 Notes/Operator_evolution/operator_evolution.tex
Update operator_evolution.tex
Updated a couple minor typos in figure captions.

%
\begin{figure*}[tbh]
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{deuteron_momentum_distributions_kvnn111.pdf}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300,0_momentum_distributions_kvnn111.pdf}%
	}
	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential. Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dashed) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted). Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
	\label{fig:momentum_distributions_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3,\mbox{fm}^{-1}$.
	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.
	The dotted lines indicate the value of $|\psi^A_{\infty}(q)|^2 / |\psi^B_{\infty}(q)|^2$.}
	\label{fig:R_ratio_comparison}
\end{figure*}
%

>>>>

%
\begin{figure*}[tbh]
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{deuteron_momentum_distributions_kvnn111.pdf}%
	}
	\quad
	\subfloat[]{%
	\includegraphics[clip,width=0.35\textwidth]{high_energy_state_eps300,0_momentum_distributions_kvnn111.pdf}%
	}
	\caption{Momentum distributions from deuteron (a) and a high-energy state (b) with the RKE N$^4$LO 450 MeV potential. Here, we compare SRG-evolved distributions, $G=H_D$ (red solid), $G=H_{BD}$ at $\LambdaBD=2$\,fm$^{-1}$ (blue dash-dotted), and $G=H_{BD}$ at $\LambdaBD=3$\,fm$^{-1}$ (green dash-dotted) each with $\lambda=1.5$\,fm$^{-1}$, to the initial distribution (black dotted). Also, $\varepsilon \approx 300$ MeV for the high-energy state in (b).}
	\label{fig:momentum_distributions_RKE}
\end{figure*}
%

@@

%
\begin{figure*}[tbh]
	\includegraphics[clip,width=0.75\textwidth]{momentum_projection_ratios_q3,00_3S1_Wegner_kvnns_111_79_6_222.pdf}%
	\caption{Ratio of evolved matrix elements $R[\ataq(k,k)]$ (diagonal) and $R[\ataq(k,0)]$ (full off-diagonal) as defined in \eqref{eq:momentum_proj_matrix_elements_ratio} in the $^3$S$_1$ channel for $q = 3\,\mbox{fm}^{-1}$.
	Three potentials are compared to RKE N$^4$LO after evolution to several values of $\lambda$ with $G = H_D$.
	The dotted lines indicate the value of $|\psi^A_{\infty}(q)|^2 / |\psi^B_{\infty}(q)|^2$.}
	\label{fig:R_ratio_comparison}
\end{figure*}
%
